---
title: CMT2A
subtitle: Changing Reference Levels in the Cox Proportional Hazards Model Table
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Table

For changing the reference levels, for example to use placebo as reference for a treatment arm variable, we can just reorder the levels of the corresponding factor variables, and pass the resulting dataset to the model fitting function as before.
The `forcats` package provides convenience functions for the level reordering.

```{r}
adtte2 <- adtte %>%
  mutate(
    ARM = forcats::fct_relevel(
      ARM,
      "B: Placebo",
      "C: Combination",
      "A: Drug X"
    )
  )
```

Now we can proceed in the same way as in [CMT2](cmt02.qmd).

```{r}
result <- basic_table() %>%
  summarize_coxreg(
    variables = list(
      time = "AVAL",
      event = "is_event",
      arm = "ARM",
      covariates = c("AGE", "BMRKR1", "BMRKR2")
    ),
    multivar = TRUE
  ) %>%
  append_topleft("Effect/Covariate Included in the Model") %>%
  build_table(adtte2)

result
```

{{< include ../../session_info.qmd >}}
:::
