---
title: RFG2A
subtitle: Response Forest Graphs for Comparing Continuous Biomarker Effects Across Subgroups (Multiple Continuous Biomarkers)
categories: [RFG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

Here we specify that we would like to analyze the two continuous biomarkers `BMRKR1` and `AGE`, conditional on the covariate `SEX`, in the subgroups defined by the levels of `BMRKR2`.

```{r}
df <- extract_rsp_biomarkers(
  variables = list(
    rsp = "COMPRESP",
    biomarkers = c("BMRKR1", "AGE"),
    covariates = "SEX",
    subgroups = "BMRKR2"
  ),
  data = adrs_f
)

result <- tabulate_rsp_biomarkers(df, vars = c("n_tot", "n_rsp", "prop", "or", "ci"))
```

We can look at the result in the console already.

```{r}
result
```

Note that in addition to the `Categorical Level Biomarker 2` subgroups we automatically also get the estimates for the overall patient population.

We can then produce the final forest plot using the `g_forest()` function on this tabular result.

```{r, fig.width = 15}
g_forest(result, xlim = c(0.7, 1.4))
```

{{< include ../../misc/session_info.qmd >}}
:::
