---
title: RG3
subtitle: Response Graphs Comparing BEP vs. Overall Population
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

In this example we can use the `facet_grid()` layer with the `margins = TRUE` option to compare the responses between the biomarker evaluable population (BEP) and the overall population.

```{r}
graph <- ggplot(adrs, aes(BMEASIFL, fill = AVALC_BIN, by = BMEASIFL)) +
  geom_bar(position = "fill") +
  geom_text(stat = "prop", position = position_fill(.5), colour = "white") +
  scale_y_continuous(
    labels = scales::percent,
    name = "Proportion %"
  ) +
  scale_x_discrete(labels = NULL) +
  xlab(NULL)

graph +
  facet_grid(BEP01FL ~ ., margins = TRUE)
```

In this example we compare the responses across treatment arms between the biomarker evaluable population and the full population.
We can add the option `margins = TRUE` option within the `facet_grid()` layer to obtain the responses across all treatment arms and their combination within each of the populations.

```{r}
graph +
  facet_grid(BEP01FL ~ ARM_BIN, margins = TRUE)
```

{{< include ../../session_info.qmd >}}
:::
