---
title: DG3A
subtitle: Barplot of a Categorical Variable by Another Categorical Variable
categories: [DG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

Here below the code for a simple distribution of the category counts of a first biomarker variable (`BMRKR2`) split by a second categorical variable (`ARM`).
We can use again the `facet_grid()` layer.

```{r}
graph <- ggplot(adsl, aes(BMRKR2)) +
  geom_bar() +
  facet_grid(. ~ ARM)

graph
```

We could instead display the columns next to each other within the same graph with the `fill` aesthetic and the `position_dodge()` option instead of using the `facet_grid()` layer.

```{r}
graph <- ggplot(adsl, aes(ARM, fill = BMRKR2)) +
  geom_bar(position = position_dodge())

graph
```

We can then again add the absolute count above each of the columns.

```{r}
graph +
  geom_text(
    stat = "count",
    aes(label = after_stat(count)),
    position = position_dodge(0.9),
    vjust = -.5
  )
```

{{< include ../../misc/session_info.qmd >}}
:::
