---
title: SFG3A
subtitle: Comparing Between Genders in Survival Forest Graph for One Treatment Arm
categories: [SFG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

We prepare the data similarly as in [SFG3](sfg03.qmd).
Additionally we are filtering `synthetic_cdisc_data$adtte` to keep only two categories for the `SEX` variable (otherwise we would not be able to do the forest plot), and we are keeping all ITT patients.
We then tabulate statistics to be able to use them as an input for the forest plot.

```{r}
adtte_mf <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adtte %>%
  df_explicit_na() %>%
  filter(
    PARAMCD == "OS",
    ARM == "A: Drug X",
    SEX %in% c("M", "F")
  ) %>%
  droplevels() %>%
  mutate(
    AVAL = day2month(AVAL),
    AVALU = "Months",
    is_event = CNSR == 0
  ) %>%
  var_relabel(
    BEP01FL = "BEP",
    BMRKR1 = "Biomarker (Countinuous)"
  )

tbl <- extract_survival_subgroups(
  variables = list(
    tte = "AVAL",
    is_event = "is_event",
    arm = "SEX",
    subgroups = "BEP01FL"
  ),
  label_all = "ITT",
  data = adtte_mf
)

result <- basic_table() %>%
  tabulate_survival_subgroups(
    df = tbl,
    vars = c("n_tot_events", "n", "n_events", "median", "hr", "ci"),
    time_unit = adtte_mf$AVALU[1]
  )
```

We can now produce the forest plot using the `g_forest()` function.

```{r, fig.width = 15}
g_forest(result)
```

{{< include ../../misc/session_info.qmd >}}
:::
