---
title: DG2
subtitle: Boxplots of a Numeric Variable by Categorical Variables
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

The graph below plots the distribution of a biomarker variable (on a continuous scale) as a boxplot by one or more categorical clinical variables with overlaid points.

We will use the `synthetic_cdisc_data$adsl` data set from the `scda` package to illustrate the graph and will select the biomarker evaluable population with `BEP01FL`.
The column `BMRKR1` contains the biomarker values on a continuous scale.
We will use `STRATA2` and `ARM` as categorical clinical variables.

```{r, message = FALSE}
library(tern)
library(ggplot2.utils)
library(dplyr)

adsl <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adsl %>%
  df_explicit_na() %>%
  filter(BEP01FL == "Y")
```

## Standard Plot

Here below the code for a simple boxplot with the outliers displayed.
Note that you may run into warning messages after producing the graph if the variable you want to analyze contains NAs.
To avoid these warning messages, you can use the `drop_na()` function from `tidyr` in the data manipulation step above to remove the NAs rows from the dataset (e.g `drop_na(BMRKR1)`).

```{r}
graph <- ggplot(adsl, aes(x = STRATA2, y = BMRKR1)) +
  geom_boxplot() +
  stat_boxplot(geom = "errorbar")

graph
```

Now we overlay the original data points, and remove the display of the outliers to avoid duplicate points.

```{r}
graph <- ggplot(adsl, aes(x = STRATA2, y = BMRKR1)) +
  geom_boxplot(outlier.shape = NA) +
  stat_boxplot(geom = "errorbar") +
  geom_point(
    position = position_jitter(width = 0.2),
    alpha = 1 / 4
  )

graph
```

We can customize the labels of the axes.

```{r}
graph +
  scale_x_discrete(
    breaks = c("S1", "S2"),
    labels = c("Stratum 1", "Stratum 2"),
    name = "Strata"
  ) +
  scale_y_continuous(name = "Biomarker (Units)")
```

We can add the group sizes as annotations.

```{r}
graph +
  stat_n_text(text_box = TRUE)
```

We can also display the biomarker by a further categorical variable with the `facet_grid()` layer.

```{r}
graph +
  facet_grid(. ~ ARM)
```

This example shows how to display the biomarker axis on a log scale.

```{r}
graph +
  scale_y_log10(name = "Biomarker (Log(Units))")
```

{{< include ../session_info.qmd >}}
:::
