---
title: DG4
subtitle: Scatterplots of Two Numerical Variables
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

The graph below plots two continuous (biomarker) variables against each other.

We will use the `synthetic_cdisc_data$adsl` data set from the `scda` package to illustrate the graph and will select the biomarker evaluable population with `BEP01FL`.
The columns `AGE` and `BMRKR1` contain the biomarker values of interest on a continuous scale.

```{r, message = FALSE}
library(tern)
library(ggplot2.utils)
library(dplyr)

adsl <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adsl %>%
  df_explicit_na() %>%
  filter(BEP01FL == "Y")
```

## Plot

Here is an example first on the original scale.
Note that you may run into warning messages after producing the graph if the continuous variable you want to analyze contains NAs.
To avoid these warning messages, you can use the `drop_na()` function from `tidyr` in the data manipulation step above to remove the NAs rows from the dataset (e.g `drop_na(AGE, BMRKR1)`).

```{r}
graph <- ggplot(adsl, aes(x = AGE, y = BMRKR1)) +
  geom_point()

graph +
  labs(x = "Age (Years)", y = "Biomarker (Units)")
```

We can also plot it on a log scale.

```{r}
graph +
  scale_y_log10() +
  labs(x = "Age (Years)", y = "Biomarker (Log(Units))")
```

{{< include ../session_info.qmd >}}
:::
