---
title: KG3
subtitle: Kaplan-Meier Graphs by Biomarker Subgroups
categories: [KG]
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

The same data set as in [KG1A](../graphs/KG1/kg01a.qmd) is used.
The difference is that here we use the categorical biomarker variable `BMRKR2` as the treatment arm in `variables` which is then used by `g_km()` below.

```{r, message = FALSE}
library(tern)
library(dplyr)

adtte_arm_bep <- random.cdisc.data::cadtte %>%
  df_explicit_na() %>%
  filter(PARAMCD == "OS", ARM == "A: Drug X", BEP01FL == "Y") %>%
  mutate(is_event = CNSR == 0)

variables <- list(tte = "AVAL", is_event = "is_event", arm = "BMRKR2")
```

## Plot

We can produce the basic plot using the `g_km()` function from `tern`.

```{r, fig.width=9, fig.height=6}
g_km(
  df = adtte_arm_bep,
  variables = variables,
  annot_surv_med = FALSE
)
```

We can also choose to annotate the plot with the median survival time for each of the biomarker subgroups using the `annot_surv_med = TRUE` option.

```{r, fig.width=9, fig.height=6}
g_km(
  df = adtte_arm_bep,
  variables = variables,
  annot_surv_med = TRUE
)
```

{{< include ../misc/session_info.qmd >}}
:::
