---
title: RG2
subtitle: Response Graphs by Treatment Arms
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

The same setup as in [RG1](../graphs/rg01.qmd) is used.

For `ggplot()` used in all analyses, we add `by = BMEASIFL` in the aesthetics to support the calculation of proportions using `geom_text(stat = "prop")`.

```{r, message = FALSE}
library(tern)
library(ggplot2.utils)
library(dplyr)

adrs <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adrs %>%
  df_explicit_na() %>%
  mutate(AVALC = ordered(AVALC, levels = c("<Missing>", "NE", "PD", "SD", "PR", "CR"))) %>%
  filter(PARAMCD == "BESRSPI", BMEASIFL == "Y")
```

## Standard Plot

The `facet_grid()` layer from `ggplot2` can be used to plot response by treatment arm and the `margins` argument can be used to produce the `(all)` column.

```{r}
graph <- ggplot(adrs, aes(BMEASIFL, fill = AVALC, by = BMEASIFL)) +
  geom_bar(aes(BMEASIFL), position = "fill") +
  geom_text(stat = "prop", position = position_fill(.5)) +
  scale_y_continuous(labels = scales::percent) +
  ylab("%") +
  facet_grid(. ~ ARM, margins = TRUE)

graph
```

## Binarize Response Outcome for Response Graph by Treatment Arms (RG2A)

We can use the `fct_collapse_only()` function from `tern` to binarize the response variable.

```{r}
adrs <- adrs %>%
  mutate(
    AVALC_BIN = fct_collapse_only(
      AVALC,
      Yes = c("CR", "PR"),
      No = c("PD", "SD", "NE", "<Missing>")
    )
  )
```

We can then produce the response plot with the newly binarized response variable.

```{r}
graph <- ggplot(adrs, aes(BMEASIFL, fill = AVALC_BIN, by = BMEASIFL)) +
  geom_bar(aes(BMEASIFL), position = "fill") +
  geom_text(stat = "prop", position = position_fill(.5)) +
  scale_y_continuous(labels = scales::percent) +
  ylab("%") +
  facet_grid(. ~ ARM, margins = TRUE)

graph
```

Note that colors and horizontal plotting is possible as described in [RG1B, RG1C](../graphs/rg01.qmd).

{{< include ../session_info.qmd >}}
:::
