---
title: DT1
subtitle: Demographics Tables Comparing BEP vs. Overall Population
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

The tables below compare the overall population ("All") with the biomarker evaluable population ("BEP") with regards to selected demographic variables.

We will use the `synthetic_cdisc_data$adsl` data set from the `scda` package to illustrate the tables.
We add a second artificial BEP flag variable `BEP02FL`.

In order to compare All with BEP, we need to define a list `bep_groups` defining these two groups.
The reason is that these two groups are overlapping (BEP is a subset of All).
Here, we refer in the list elements to the levels `Y` and `N` of the biomarker population flag variable `BEP01FL` from `adsl` which we will use below:

```{r, message = FALSE}
library(tern)
library(dplyr)

set.seed(123)
adsl <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adsl %>%
  df_explicit_na() %>%
  mutate(BEP02FL = factor(sample(c("Y", "N"), size = n(), replace = TRUE)))

bep_groups <- list(
  "All" = c("Y", "N"), 
  "BEP" = "Y"
)
```

This can then be used by the `tern` layout function `split_cols_by_groups()` below.

## Table

The simplest demographics table DT1 splits the columns by treatment arm and All vs. BEP, and summarizes selected demographic variables in the rows.

```{r}
lyt <- basic_table() %>%
  split_cols_by("ARM") %>%
  split_cols_by_groups("BEP01FL", bep_groups) %>%
  summarize_vars(c("AGE", "SEX")) %>%
  add_colcounts()

build_table(lyt, adsl)
```

## Reorder Treatment Arms in Demographics Table (DT1A)

We can reorder the treatment arm columns in the demographics table DT1 by using the `reorder_split_levels()` splitting function in `split_cols_by()` as done here.

```{r}
lyt <- basic_table() %>%
  split_cols_by("ARM", split_fun = reorder_split_levels(c("B: Placebo", "A: Drug X", "C: Combination"))) %>%
  split_cols_by_groups("BEP01FL", bep_groups) %>%
  summarize_vars(c("AGE", "SEX")) %>%
  add_colcounts()

build_table(lyt, adsl)
```

## Combine Treatment Arms in Demographics Table (DT1B)

It is simple to omit the treatment arm split in the demographics table DT1, thus effectively combining the treatment arms.

```{r}
lyt <- basic_table() %>%
  split_cols_by_groups("BEP01FL", bep_groups) %>%
  summarize_vars(c("AGE", "SEX")) %>%
  add_colcounts()

build_table(lyt, adsl)
```

## Alternative BEP Indicator in Demographics Table (DT1C)

We can of course use a different BEP factor variable `BEP02FL` with corresponding groups definition `bep2_groups` in the demographics table DT1.

```{r}
bep2_groups <- list(
  "All" = c("Y", "N"), 
  "BEP2" = "Y"
)

lyt <- basic_table() %>%
  split_cols_by("ARM") %>%
  split_cols_by_groups("BEP02FL", bep2_groups) %>%
  summarize_vars(c("AGE", "SEX")) %>%
  add_colcounts()

build_table(lyt, adsl)
```

{{< include ../session_info.qmd >}}
:::
