---
title: TET1
subtitle: Time-to-Event Summary Tables
---

------------------------------------------------------------------------

::: panel-tabset
## Setup

We will use the `synthetic_cdisc_data$adtte` data set from the `scda` package for the time-to-event summary table.
We start by filtering the `adtte` data set for the overall survival observations, converting time of overall survival to months, creating new variables for event and non-event information and binarizing the `ARM` variable.

```{r, message = FALSE}
library(tern)
library(dplyr)

adtte <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adtte %>% 
  df_explicit_na() %>%
  filter(
    PARAMCD == "OS"
  ) %>%
  mutate(
    AVAL = day2month(AVAL),
    AVALU = "Months",
    is_event = CNSR == 0,
    is_not_event = CNSR == 1,
    ARM_BIN = fct_collapse_only(
      ARM,
      CTRL = c("B: Placebo"),
      TRT = c("A: Drug X", "C: Combination")
    )
  )
```

## Table

This time-to-event summary table splits the columns by treatment arm using `split_cols_by()`, creates a summary for patients with and without event using `summarize_vars()`, summarizes survival time using `surv_time()` and summarizes the analysis from unstratified Cox Proportional Hazards models using `coxph_pairwise()`.

```{r}
lyt <- basic_table() %>% 
  split_cols_by(
    var = "ARM_BIN",
    ref_group = "CTRL"
  ) %>% 
  add_colcounts() %>% 
  summarize_vars(
    vars = "is_event",
    .stats = "count_fraction",
    .labels = c(count_fraction = "Patients with event (%)"),
    nested = FALSE,
    show_labels = "hidden"
  ) %>% 
  summarize_vars(
    vars = "is_not_event",
    .stats = "count_fraction",
    .labels = c(count_fraction = "Patients without event (%)"),
    nested = FALSE,
    show_labels = "hidden"
  ) %>% 
  surv_time(
    vars = "AVAL",
    var_labels = "Time to Event (months)",
    is_event = "is_event",
    table_names = "time_to_event"
  ) %>% 
  coxph_pairwise(
    vars = "AVAL",
    is_event = "is_event",
    var_labels = c("Unstratified Analysis"),
    control = control_coxph(pval_method = "log-rank"),
    table_names = "coxph_unstratified"
  )

build_table(lyt, adtte)
```

## Time-to-Event Summary Table with Stratified Analysis (TET1A)

We can add the summary of an analysis with Cox Proportional Hazards models stratified by `SEX` to the table above using `coxph_pairwise()`.

```{r}
lyt2 <- lyt %>% 
  coxph_pairwise(
    vars = "AVAL",
    is_event = "is_event",
    var_labels = c("Stratified Analysis"),
    strat = "SEX",
    control = control_coxph(pval_method = "log-rank"),
    table_names = "coxph_stratified"
  ) 

build_table(lyt2, adtte)
```

{{< include ../session_info.qmd >}}
:::
