---
title: SFG6A
subtitle: Survival Forest Graph for Multiple Continuous Biomarkers
categories: [SFG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

Here we specify that we would like to analyze the two continuous biomarkers `BMRKR1` and `AGE`, conditional on the covariate `SEX`, in the subgroups defined by the levels of `BMRKR2`.

```{r}
df <- extract_survival_biomarkers(
  variables = list(
    tte = "AVAL",
    is_event = "is_event",
    biomarkers = c("BMRKR1", "AGE"),
    covariates = "SEX",
    subgroups = "BMRKR2"
  ),
  data = adtte_f
)

result <- tabulate_survival_biomarkers(
  df = df,
  vars = c("n_tot_events", "n_tot", "median", "hr", "ci"),
  time_unit = adtte_f$AVALU[1]
)
```

We can look at the result in the console already.

```{r}
result
```

Note that in addition to the `Categorical Level Biomarker 2` subgroups we automatically also get the estimates for the overall patient population in the `All Patients` rows.

We can then produce the final forest plot using the `g_forest()` function on this tabular result.

```{r, fig.width = 15}
g_forest(result, xlim = c(0.7, 1.4))
```

Here we can see that the continuous biomarker (`BMRKR1`) shows a trend towards an estimated positive effect on survival (it is not statistically significant though as the confidence intervals still overlap the hazard ratio 1).
It is a bit easier to see this here rather than in a cutpoint analysis as presented in [SFG3](../../graphs/SFG3/sfg03.qmd).

{{< include ../../misc/session_info.qmd >}}
:::
