---
title: SFG1
subtitle: Survival Forest Graphs for Overall Population and by Categorical Biomarker
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

We use the `extract_survival_subgroups()` function to calculate the survival forest results for the subgroups defined by the levels of the factor variables given in `subgroups`.
We then tabulate the estimated statistics with the function `tabulate_survival_subgroups()` to be able to use them as an input for forest plot.
Note that for the argument `vars` we could select different statistics, but the statistics `n_tot`, `hr` and `ci` are required.

```{r}
tbl <- extract_survival_subgroups(
  variables = list(
    tte = "AVAL",
    is_event = "is_event",
    arm = "ARM_BIN",
    subgroups = c("BEP01FL", "BMRKR2")
  ),
  label_all = "ITT",
  data = adtte
)

result <- basic_table() %>%
  tabulate_survival_subgroups(
    df = tbl,
    vars = c("n_tot_events", "n", "n_events", "median", "hr", "ci"),
    time_unit = adtte$AVALU[1]
  )
```

We can remove the last line showing the `<Missing>` category from the `result` table to display the survival forest plot only with non-missing categories for `BMRKR2`.

```{r}
result <- result[-9, , keep_topleft = TRUE]
```

We can now produce the forest plot using the `g_forest()` function from `tern` based on this trimmed `result` table.

```{r, fig.width = 15}
g_forest(result)
```

{{< include ../../session_info.qmd >}}
:::
