---
title: RFG1A
subtitle: Response Forest Graph Only by Categorical or Binned Continuous Biomarker
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

We define a binned factor variable `BMRKR1_cut` from the continuous biomarker variable `BMRKR1` to illustrate.
Note that the remaining code would work the same for an originally categorical biomarker.

```{r, fig.width = 15}
BMRKR1_cutpoint <- 5

adrs2 <- adrs %>%
  mutate(
    BMRKR1 = ifelse(BEP01FL == "N", NA, BMRKR1),
    BMRKR1_cut = explicit_na(factor(
      ifelse(BMRKR1 > BMRKR1_cutpoint, "Greater", "Less")
    ))
  ) %>%
  var_relabel(BMRKR1_cut = "Biomarker (Binned Continuous)")

df <- extract_rsp_subgroups(
  variables = list(
    rsp = "is_rsp",
    arm = "ARM_BIN",
    subgroups = c("BMRKR1_cut", "BMRKR2")
  ),
  data = adrs2,
  conf_level = 0.95
)

result <- basic_table() %>%
  tabulate_rsp_subgroups(df, vars = c("n_tot", "n", "n_rsp", "prop", "or", "ci"))
```

We can remove the first line showing the `All Patients` category from the `result` table as follows.

```{r}
result <- result[-1, , keep_topleft = TRUE]
```

We can then produce the forest plot again using `g_forest()` on this trimmed `result` table.

```{r, fig.width = 15}
g_forest(result)
```

{{< include ../../session_info.qmd >}}
:::
