---
title: DG1A
subtitle: Histograms of Two Numeric Variables
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

In this example, we will manipulate the variables that we want to show in the graph into a long data format using the `pivot_longer()` function from `tidyr`.
This is necessary such that below we can use the faceting layer `facet_grid()` to plot each variable in its own facet.

```{r}
num_var_long <- adsl %>%
  pivot_longer(
    c(BMRKR1, BMRKR3),
    names_to = "var",
    values_to = "value"
  ) %>%
  select(var, value)
```

Producing the base plot is then simple: We use the same code as above but just add the faceting layer.

```{r}
graph <- ggplot(num_var_long, aes(value)) +
  geom_histogram(aes(y = after_stat(density)), bins = 30) +
  geom_density(aes(y = after_stat(density))) +
  facet_grid(var ~ .)

graph
```

Similar to the DG1 example, we will calculate and populate the statistics table to accompany the plot.
Note that also here we can use the `pivot_longer()` function to also obtain the statistics table input `orig_tb` and then `data_tb` in long format, and thus parallel to the biomarker variable format in `num_var_long`.

```{r}
orig_tb <- num_var_long %>%
  group_by(var) %>%
  summarize_at("value", list(mean = mean, median = median)) %>%
  pivot_longer(
    c(mean, median),
    names_to = "Statistic",
    values_to = "Value"
  )

data_tb <- orig_tb %>%
  group_by(var) %>%
  summarize(x = 1, y = 1, tb = list(tibble(Statistic, Value)))

graph <- graph +
  geom_table_npc(data = data_tb, aes(npcx = x, npcy = y, label = tb))

graph
```

{{< include ../../session_info.qmd >}}
:::
