---
title: DG1
subtitle: Histograms of Numeric Variables
categories: [DG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

In this example, we will create a combined histogram/density graph of a continuous biomarker variable.
Note that you may run into warning messages after producing the graph if the variable you want to analyze contains NAs.
To avoid these warning messages, you can use the `drop_na()` function from `tidyr` in the data manipulation step above to remove the NAs rows from the dataset (e.g `drop_na(BMRKR1)`).

```{r}
graph <- ggplot(adsl, aes(BMRKR1)) +
  geom_histogram(aes(y = after_stat(density)), bins = 30) +
  geom_density(aes(y = after_stat(density)))

graph
```

We can also calculate some descriptive statistics and populate a table that we can overlay on top of the plot.
The `tibble` function is used to build a data frame `data_tb` with 3 variables.
The `x` and `y` variables represent the coordinates on the plot to show the statistic values and can be modified based on preference.
For example, `x = 1` and `y = 1` will put the statistics table in the top right corner of the graph, while `x = 0` and `y = 0` will put the statistics table in the bottom left corner of the graph.
The `tb` variable contains the statistics to be shown on the plot, in the form of a nested list column starting from the original statistics tibble `orig_tb`.
Finally, we can use the `geom_table_npc()` layer function to process the `data_tb` input and add the statistics table to the existing graph.

```{r}
orig_tb <- with(adsl, tribble(
  ~Statistic, ~Value,
  "N", length(BMRKR1),
  "SD", sd(BMRKR1),
  "Median", median(BMRKR1),
  "Min.", min(BMRKR1),
  "Max.", max(BMRKR1)
))

data_tb <- tibble(x = 1, y = 1, tb = list(orig_tb))

graph <- graph +
  geom_table_npc(data = data_tb, aes(npcx = x, npcy = y, label = tb))

graph
```

{{< include ../../misc/session_info.qmd >}}
:::
