---
title: KG1B
subtitle: Kaplan-Meier Graph for Comparing ITT and BEP Populations
categories: [KG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

Here we only filter the time-to-event dataset for the overall survival observations, but keep all treatment arms and the overall population.

```{r}
adtte <- scda::synthetic_cdisc_data("rcd_2022_06_27")$adtte %>%
  df_explicit_na() %>%
  filter(PARAMCD == "OS") %>%
  mutate(is_event = CNSR == 0)

variables <- list(tte = "AVAL", is_event = "is_event", arm = "ARM")
```

First create a new empty plot, and then setup a `grid` layout to allow plotting several KM curves on a single graph device.
Once the `grid` layout is defined, plot the ITT (top, with CIs) and BEP (bottom, without CIs) KM graphs.
Note that these steps need to executed in the order specified below to enable creation of these plots in one graph.

```{r, fig.width = 15, fig.height = 12}
plot.new()
lyt <- grid.layout(nrow = 2, ncol = 1) %>%
  viewport(layout = .) %>%
  pushViewport()

res <- g_km(
  df = adtte, variables = variables, newpage = FALSE, annot_surv_med = FALSE,
  ci_ribbon = TRUE,
  vp = viewport(layout.pos.row = 1, layout.pos.col = 1)
)

res <- g_km(
  df = filter(adtte, BEP01FL == "Y"), variables = variables, newpage = FALSE, annot_surv_med = FALSE,
  vp = viewport(layout.pos.row = 2, layout.pos.col = 1)
)
```

{{< include ../../misc/session_info.qmd >}}
:::
