---
title: KG1B
subtitle: Kaplan-Meier Graph for Comparing ITT and BEP Populations
categories: [KG]
---

------------------------------------------------------------------------

::: panel-tabset
{{< include setup.qmd >}}

## Plot

Here we only filter the time-to-event dataset for the overall survival observations, but keep all treatment arms and the overall population.

```{r}
adtte <- random.cdisc.data::cadtte %>%
  df_explicit_na() %>%
  filter(PARAMCD == "OS") %>%
  mutate(is_event = CNSR == 0)

variables <- list(tte = "AVAL", is_event = "is_event", arm = "ARM")
```

Plot the ITT (top, with CIs) and BEP (bottom, without CIs) KM graphs, convert them to `ggplotGrob` objects, and combine the plots via `rbind`.
Then, use the `grid` package to create an empty plot area, and draw the KM curves on the graph device.

```{r, fig.width=9, fig.height=12}
res1 <- g_km(
  df = adtte, variables = variables, annot_surv_med = FALSE, ci_ribbon = TRUE
)

res2 <- g_km(
  df = filter(adtte, BEP01FL == "Y"), variables = variables, annot_surv_med = FALSE
)

g <- rbind(ggplot2::ggplotGrob(res1), ggplot2::ggplotGrob(res2), size = "first")

grid.newpage()
grid.draw(g)
```

{{< include ../../misc/session_info.qmd >}}
:::
